On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-26 Manuscript/manuscript.tex
Applied AJUR Format, Still have to make some changes

\documentclass[12pt, letterpaper, titlepage]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref, url}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor =
  blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}

\usepackage[pagewise]{lineno}
%\linenumbers*[1]
% %% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
 \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
 \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
 \renewenvironment{#1}%
 {\linenomath\csname old#1\endcsname}%
 {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
 \patchAmsMathEnvironmentForLineno{#1}%
 \patchAmsMathEnvironmentForLineno{#1*}}%

\AtBeginDocument{%
 \patchBothAmsMathEnvironmentsForLineno{equation}%
 \patchBothAmsMathEnvironmentsForLineno{align}%
 \patchBothAmsMathEnvironmentsForLineno{flalign}%
 \patchBothAmsMathEnvironmentsForLineno{alignat}%
 \patchBothAmsMathEnvironmentsForLineno{gather}%
 \patchBothAmsMathEnvironmentsForLineno{multline}%
}

% control floats
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

\title{On Sample Size for Block Bootstrap Confidence Intervals 
  to Have Desired Coverage Rates}

\author{Mathew Chandy, Elizabeth Schifano,
%   \href{mailto:mathew.chandy@uconn.edu}
% {\nolinkurl{mathew.chandy@uconn.edu}}\\
  and Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}

\begin{document} 
\maketitle

\begin{abstract}
Block bootstrap is widely used in constructing confidence intervals for 
parameters estimated from stationary time series. Theoretically, the method
should provide valid confidence intervals as the length of the time series goes
to infinity. In practice, however, it is necessary to know how large of a finite 
sample is required for block bootstrap confidence intervals to work well. This 
study aims to answer this question in a simple simulation setting where the data 
are generated from a first-order autoregressive process. The empirical coverage 
rates of several commonly used bootstrap confidence intervals for the mean, 
standard deviation, and the lag-1 autocorrelation coefficient are compared. A 
quite large sample is found necessary for the intervals to have the right 
coverage rates even when estimating a simple parameter like the mean. Some block 
bootstrap methods could fail when estimating the lag-1 autocorrelation. It is 
surprising that the coverage property even deteriorates as the sample size 
increases with some commonly used block bootstrap confidence intervals including 
the percentile intervals and bias-corrected intervals.

\bigskip
\noindent{\sc Keywords}:
dependent data; resampling; simulation; time series
\end{abstract}

\doublespace

\section{Introduction}
\label{sec:intro}

@@

The remainder of the paper is organized as follows. Section~\ref{sec:bbci} 
reviews block bootstrap procedures and how to use block bootstrap estimates to
construct CIs; a simple CI obtained by recentering at the original point 
estimate is proposed for comparison. Section~\ref{sec:simu} reports a simulation 
study comparing the coverage rates of six block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

\section{Block Bootstrap CIs}
\label{sec:bbci}

@@

\subsection{Block Bootstrap}

@@

\subsection{Block Bootstrap CIs}

@@

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\]
Define
\[
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\text{ and }
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

\paragraph{Recentered Percentile CI}
We propose a CI that is centered at the original point estimate and uses the 
variation in the bootstrap estimates to construct the error bound. This interval 
requires
the computation of $\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the 
mean of all bootstrap point estimates. A $(1 - \alpha)100\%$ CI is
centered around $\hat\theta_n$ and can be rewritten as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{B} - \bar\theta_n^{B}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{B} - \bar\theta_n^{B}).
\]
It is not necessarily symmetric, as different critical values are used to 
compute the lower and upper bounds. It has the same width as the percentile CI.

\section{Simulation Study}
\label{sec:simu}

\subsection{Design}
We designed a simulation study to compare the performance of the different block 
bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
order auto-regressive (AR(1)) process:
\[
X_t = \phi X_{t-1} + \epsilon_t,
\]
where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
CIs for each parameter as described in the last section. We can estimate $\mu$, 
$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
and lag-1 auto-correlation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in Section~\ref{sec:bbci}. Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot} \citep{boot}, with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and $l = \lceil n^{1/3} \rceil$.

The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
expected to match the nominal level. Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% CI of the coverage rate 
(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. Figures~\ref{fig:mu}--\ref{fig:phi} summarizes the 
empirical coverage rates and the 95\% confidence intervals of the real coverage, 
generated using the R \textsl{ggplot2} package \citep{ggplot2}.

@@

\subsection{Results}

For estimating the mean parameter~$\mu$, Figure~\ref{fig:mu} suggests that all
methods eventually approach correct coverage of $\mu$ as sample size increases. 
Student's $t$ CIs appear to need the smallest sample size to achieve correct 
coverage, except for samples with strong negative dependence, in which case, 
they actually over-cover $\mu$ for smaller sample sizes. For instance, for a 
sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ CI's 
coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for other 
methods contain 95\%. The standard, percentile, BC, and BCA, and recentered 
percentile CIs require similar sample sizes to recover $\mu$ at the nominal 
level for all combinations of $n$ and $\phi$. All methods seem to require a 
smaller sample to recover $\mu$ at the nominal rate when dealing with negative 
dependence versus positive dependence. For example, BC CIs recover $\mu$ for 
$n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for $n \geq 800$ 
when $\phi = 0.2$. In addition, as a negative dependence gets stronger, holding 
everything else equal, coverage increases, which lead to the Student $t$ CI's 
aforementioned over-coverage. As a positive dependence gets stronger, holding 
everything else equal, coverage decreases, and a larger sample is necessary to 
recover~$\mu$.

For estimating the standard deviation parameter~$\sigma_x$,
Figure~\ref{fig:sigma} suggests that every method can reach nominal coverage of
$\sigma_x$ if the sample is large enough, but for a given $n$ and $\phi$,
coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general. Like 
$\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample sizes
when compared to other methods. Unlike $\mu$, there is no over-coverage issue 
for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and recentered 
percentile CIs again have similar performance. All methods seem to have slightly 
higher coverage of $\sigma_x$ when $\phi$ is negative versus when $\phi$ is 
positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as the 
strength of the temporal dependence increases.

For estimating the auto-correlation parameter~$\phi$, Figure~\ref{fig:phi}
suggests that while standard, Student's $t$, and recentered percentile CIs do
approach correct coverage as sample size increases, percentile, BC, and BCA CIs 
deteriorate as sample size increases, especially as the strength of the temporal 
dependence increases. Because of this, only standard, Student's $t$, and 
recentered percentile CIs should be considered as effective block bootstrap 
methods to estimate $\phi$. Student's $t$ CIs once again can achieve correct
coverage with smaller sample sizes when compared to standard and recentered 
percentile CIs which perform similarly. Student's $t$ CIs can can recover $\phi$ 
at the nominal level for $n \geq 100$ when the sample's temporal dependence is 
as strong as 0.4. Coverage appears to be higher for all methods when the
dependence is negative rather than positive. Whether or not the dependence is
negative or positive, coverage of $\phi$ seems to increase slightly as the
absolute value increases for standard, Student's $t$, and recentered percentile
CIs. For the values of $\phi$ observed, there are no examples of over-coverage 
for standard, Student's $t$, BC, BCA, or recentered percentile CIs. However, 
percentile CIs appear to over-cover $\phi$ for smaller sample sizes when 
$\phi = -0.2$ and when $\phi = 0$, indicating again that they should not be used.

@@

The outcomes of the $\phi$ estimation raise a natural question about the 
lackluster performance of certain methodologies. To delve into this inquiry, a
set of 50 CIs was generated for each of the percentile, BC, and recentered
percentile  approaches for samples of $n \in \{800, 1600\}$. Illustrated in 
Figure~\ref{fig:npi}, it becomes evident that the percentile-based CIs exhibit a 
notable bias, predominantly manifesting as a substantial underestimation of 
$\phi$ with point estimator $\bar\theta_n^B$, that is, the average of $B$ 
bootstrap point estimates. As the sample size increases from 800 to 1600, this 
bias does not vanish while the uncertainty reduces, which explains why the 
coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
invalidate the bias-correction in the BC bootstrap, leading to the poor 
performance of the BC intervals. The BCA intervals have the same problem as the 
BC intervals in the bias-correction step. The root of the issue appears to be 
that the autocorrelation in the block bootstrap samples is somehow smaller 
compared to that in the original sample. On the other hand, the original point 
estimate $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
the uncertainty in the bootstrap point estimates $\hat\theta_n^{(b)}$, 
$b = 1, \ldots, B$, the percentile CIs recentered at the original point estimate
$\hat\theta_n$ provide desired coverage.

@@

\section{Discussion}
\label{sec:disc}

@@

\eds{Check out this paper:
Peter Buhlmann. "Bootstraps for Time Series." Statist. Sci. 17(1) 52 - 72, 
May 2002 - the conclusions of this paper are interesting in their own right:
``Disadvantages of the [block bootstrap] method include the following.
The block bootstrap sample should not be viewed as
a reasonable sample mimicking the data-generating
process: it is not stationary and exhibits artifacts where
resampled blocks are linked together. This implies that
the plug-in rule for bootstrapping an estimator $\hat{\theta}$ is not
appropriate. A prevectorization of the data is highly
recommended, but the bootstrapped estimator and its
computing routine may then need to be redesigned. As
a general nonparametric scheme, the block bootstrap
may be outperformed in various niches of stationary
time series, for example, for linear time series (see Section 3) 
and for categorical processes (see Section 5).
Second-order accuracy for a confidence interval has
been justified with the approach of Studentizing and
BCA correction (in the case of noncategorical time series); 
the latter was found to yield marginal improvement in a 
simulated example (we did not consider the former). } \mc{addressed}

>>>>

% Created by Bonita Graham
% Last update: December 2019 By Kestutis Bendinskas

% Authors: 
% Please do not make changes to the preamble until after the solid line of %s.

\documentclass[10pt]{article}
\usepackage[explicit]{titlesec}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\usepackage{hyphenat}
\usepackage{ragged2e}
\RaggedRight

% These commands change the font. If you do not have Garamond on your computer, you will need to install it.
\usepackage{garamondx}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amsthm}
\usepackage{graphicx}

% This adjusts the underline to be in keeping with word processors.
\usepackage{soul}
\setul{.6pt}{.4pt}

% The following sets margins to 1 in. on top and bottom and .75 in on left and right, and remove page numbers.
\usepackage{geometry}
\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{gobble}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}

% These Commands create the label style for tables, figures and equations.
\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
\captionsetup{labelformat=simple, labelsep=period}
\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
\renewcommand{\theequation}{\arabic{equation}}
\makeatletter
\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
\makeatother
\setlength{\intextsep}{10pt}
\setlength{\abovecaptionskip}{2pt}
\setlength{\belowcaptionskip}{-10pt}

\renewcommand{\textfraction}{0.10}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.90}

% These commands set the paragraph and line spacing
\titleformat{\section}
  {\normalfont}{\thesection}{1em}{\MakeUppercase{\textbf{#1}}}
\titlespacing\section{0pt}{0pt}{-10pt}
\titleformat{\subsection}
  {\normalfont}{\thesubsection}{1em}{\textit{#1}}
\titlespacing\subsection{0pt}{0pt}{-8pt}
\renewcommand{\baselinestretch}{1.15}

% This designs the title display style for the maketitle command
\makeatletter
\newcommand\sixteen{\@setfontsize\sixteen{17pt}{6}}
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
\sixteen\bfseries \@title
\medskip
\end{flushleft}
\textit{\@author}
\egroup}
\makeatother

% This styles the bibliography and citations.
%\usepackage[biblabel]{cite}
\usepackage[sort&compress]{natbib}
\setlength\bibindent{2em}
\makeatletter
\renewcommand\@biblabel[1]{\textbf{#1.}\hfill}
\makeatother
\renewcommand{\citenumfont}[1]{\textbf{#1}}
\bibpunct{}{}{,~}{s}{,}{,}
\setlength{\bibsep}{0pt plus 0.3ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Authors: Add additional packages and new commands here.  
% Limit your use of new commands and special formatting.

% Place your title below. Use Title Capitalization.
\title{On Sample Size for Block Bootstrap Confidence Intervals 
  to Have Desired Coverage Rates}

% Add author information below. Communicating author is indicated by an 
% asterisk, the affiliation is shown by superscripted lower case letter if 
% several affiliations need to be noted.
\author{
Mathew Chandy*$^{a}$, Elizabeth Schifano$^{a}$, Jun Yan$^{a}$ \\ \medskip 
$^{a}$Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
Student: mathew.chandy@uconn.edu* \\
Mentors: elizabeth.schifano@uconn.edu, jun.yan@uconn.edu
}
\pagestyle{empty}
\begin{document}

% Makes the title and author information appear.
\vspace*{.01 in}
\maketitle
\vspace{.12 in}

% Abstracts are required.
\section*{abstract}
Block bootstrap is widely used in constructing confidence intervals for 
parameters estimated from stationary time series. Theoretically, the method
should provide valid confidence intervals as the length of the time series goes
to infinity. In practice, however, it is necessary to know how large of a finite 
sample is required for block bootstrap confidence intervals to work well. This 
study aims to answer this question in a simple simulation setting where the data 
are generated from a first-order autoregressive process. The empirical coverage 
rates of several commonly used bootstrap confidence intervals for the mean, 
standard deviation, and the lag-1 autocorrelation coefficient are compared. A 
quite large sample is found necessary for the intervals to have the right 
coverage rates even when estimating a simple parameter like the mean. Some block 
bootstrap methods could fail when estimating the lag-1 autocorrelation. It is 
surprising that the coverage property even deteriorates as the sample size 
increases with some commonly used block bootstrap confidence intervals including 
the percentile intervals and bias-corrected intervals.

% Keywords are required.
\section*{keywords} 
List Eight to Ten Capitalized Keywords Separated by \ul{Semicolons}; Do Not Use Period at The End
Dependent Data; Resampling; Simulation; Time Series

\vspace{.12 in}

% Start the main part of the manuscript here.
% Comment out section headings if inappropriate to your discipline.
% If you add additional section or subsection headings, use an asterisk * to avoid numbering.

\section*{introduction}

@@

The remainder of the paper is organized as follows. The first section 
reviews block bootstrap procedures and how to use block bootstrap estimates to
construct CIs; a simple CI obtained by recentering at the original point 
estimate is proposed for comparison. The second section reports a simulation 
study comparing the coverage rates of six block bootstrap CIs. A discussion
concludes in the final section.

\section*{block bootstrap cis}
\label{sec:bbci}

@@

\subsection*{Block Bootstrap}

@@

\subsection*{Block Bootstrap CIs}

@@

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let 
\begin{equation}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation}
Define
\begin{equation}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation}
and
\begin{equation}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

\paragraph{Recentered Percentile CI}

We propose a CI that is centered at the original point estimate and uses the 
variation in the bootstrap estimates to construct the error bound. This interval 
requires
the computation of $\bar\theta_n^B = n^{-1}\sum_{b=1}^B \hat\theta_n^{(b)}$, the 
mean of all bootstrap point estimates. A $(1 - \alpha)100\%$ CI is
centered around $\hat\theta_n$ and can be written as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{B} - \bar\theta_n^{B}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{B} - \bar\theta_n^{B}).
\]
It is not necessarily symmetric, as different critical values are used to 
compute the lower and upper bounds. It has the same width as the percentile CI.

\section*{simulation study}
\label{sec:simu}

\subsection*{Design}
We designed a simulation study to compare the performance of the different block 
bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
order auto-regressive (AR(1)) process:
\begin{equation}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation}
where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
CIs for each parameter as described in the last section. We can estimate $\mu$, 
$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
and lag-1 auto-correlation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in \textit{Block Bootstrap CIs}. Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot} \citep{boot}, with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and $l = \lceil n^{1/3} \rceil$.

The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
expected to match the nominal level. Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% CI of the coverage rate 
(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \textbf{Figures~\ref{fig:mu}--\ref{fig:phi}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage, generated using the R \textsl{ggplot2} package \citep{ggplot2}.

@@

\subsection*{Results}

For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$.

For estimating the standard deviation parameter~$\sigma_x$,
\textbf{Figure~\ref{fig:sigma}} suggests that every method can reach nominal 
coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
$\phi$, coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general.
Like $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample 
sizes when compared to other methods. Unlike $\mu$, there is no over-coverage 
issue for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and 
recentered percentile CIs again have similar performance. All methods seem to 
have slightly higher coverage of $\sigma_x$ when $\phi$ is negative versus when 
$\phi$ is positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as 
the strength of the temporal dependence increases.

For estimating the auto-correlation parameter~$\phi$, 
\textbf{Figure~\ref{fig:phi}} suggests that while standard, Student's $t$, and 
recentered percentile CIs do approach correct coverage as sample size increases, 
percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
the strength of the temporal dependence increases. Because of this, only 
standard, Student's $t$, and recentered percentile CIs should be considered as 
effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
again can achieve correct coverage with smaller sample sizes when compared to 
standard and recentered percentile CIs which perform similarly. Student's $t$ 
CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
for all methods when the dependence is negative rather than positive. Whether or 
not the dependence is negative or positive, coverage of $\phi$ seems to increase 
slightly as the absolute value increases for standard, Student's $t$, and 
recentered percentile CIs. For the values of $\phi$ observed, there are no 
examples of over-coverage for standard, Student's $t$, BC, BCA, or recentered 
percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
should not be used.

@@

The outcomes of the $\phi$ estimation raise a natural question about the 
lackluster performance of certain methodologies. To delve into this inquiry, a
set of 50 CIs was generated for each of the percentile, BC, and recentered
percentile  approaches for samples of $n \in \{800, 1600\}$. Illustrated in 
\textbf{Figure~\ref{fig:npi}}, it becomes evident that the percentile-based CIs 
exhibit a notable bias, predominantly manifesting as a substantial 
underestimation of $\phi$ with point estimator $\bar\theta_n^B$, that is, the 
average of $B$ bootstrap point estimates. As the sample size increases from 800 
to 1600, this bias does not vanish while the uncertainty reduces, which explains 
why the coverage rates deteriorate. The bias in $\bar\theta_n^B$ also appears to 
invalidate the bias-correction in the BC bootstrap, leading to the poor 
performance of the BC intervals. The BCA intervals have the same problem as the 
BC intervals in the bias-correction step. The root of the issue appears to be 
that the autocorrelation in the block bootstrap samples is somehow smaller 
compared to that in the original sample. On the other hand, the original point 
estimate $\hat\theta_n$ is asymptotically unbiased. Since the width is based on 
the uncertainty in the bootstrap point estimates $\hat\theta_n^{(b)}$, 
$b = 1, \ldots, B$, the percentile CIs recentered at the original point estimate
$\hat\theta_n$ provide desired coverage.

@@

\section*{discussion}
\label{sec:disc}

@@
